
\documentclass[12pt,a4paper,notitlepage,twoside,openright]{report}
%\documentclass[12pt,a4paper,draft,notitlepage,twoside,openright]{report}

%Libraries for greek
\usepackage{xltxtra}
%\usepackage{xgreek} 
\setmainfont[Mapping=tex-text]{Times New Roman}
%\usepackage{cmap}
%\usepackage{ucs}
%\usepackage{kerkis}
%\usepackage[english,greek]{babel}
\usepackage[utf8x]{inputenc}

\usepackage[colorlinks=true]{hyperref} 					%hyperlinks
\hypersetup{linkcolor=blue,citecolor=blue,linktoc=page} %hyperlink options
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{setspace}
\onehalfspacing
\raggedbottom % disables vertical alignment & stretching
\setlength\parindent{0pt} %me auto den exw esoxes se kamia paragrafo (diladi noindent pantou)
\usepackage[parfill]{parskip}
\usepackage{titlesec}
\titleformat{\chapter}[display]{\normalfont\Huge\bfseries}{\chaptertitlename\ \thechapter}{15pt}{\Huge}
\titlespacing{\chapter}{0pt}{40pt}{21pt}
\titlespacing{\section}{0pt}{0pt}{0pt}
\titlespacing{\subsection}{0pt}{0pt}{0pt}
\titlespacing{\subsubsection}{0pt}{0pt}{0pt}
\usepackage{tocloft}
%\recommand\cftchapafterpnum{\vskip5pt}

\usepackage{fancyhdr} %control of page headers and footers- me auto vazw tis eutheies grammes panw kai katw stis selides
\renewcommand{\footrulewidth}{0.4pt}
%\lhead[\rm \bf \thepage]{\fancyplain{}{\sl{\rightmark}}}
\rhead{\rm \bf \thepage}{\fancyplain{}{\sl{\leftmark }}}
\chead{}\lfoot{}\rfoot{}\cfoot{}

\usepackage{graphicx}
\usepackage{amsmath} %extra math
\usepackage{mathtools}
\usepackage{amssymb} %extra symbols
\usepackage{gensymb}
\usepackage{breqn}  %break equations
\usepackage[notlof,notlot,nottoc]{tocbibind} %bibliography is not a numbered chapter
\usepackage{fixltx2e} %gia na grafw textsuperscript + textsubscript
\usepackage{enumitem} %gia to itemize
\usepackage{relsize} %gia \mathlarger + \mathsmaller
\usepackage{subcaption}
\usepackage{mwe}
\usepackage{siunitx} %gia na xrisimopoiisw to \ang{360}--> gia na valei to symvolo twn moirwn (degree)
\usepackage{textcomp}

\usepackage{algorithm}
\usepackage[noend]{algpseudocode} %gia pseudokwdika- otan thelw na perigrapsw kai kala code

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

\usepackage{amssymb}
\usepackage{longtable}

\usepackage{xr}
\usepackage{adjustbox} %auto prepei na kathorizei kai an einai i current page odd or even
\usepackage[margin=4pt,font=normalsize,labelfont=bf,textfont=it]{caption}
%\usepackage{subcaption}
%\usepackage{sidecap}
\usepackage{float}
\usepackage{ragged2e} %gia na kanei fully justified text

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % New command to make the lines in the title page

\usepackage{color} 								%hilight pachage
\usepackage[dvipsnames]{xcolor}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}} %hilight color

\usepackage[hang,flushmargin]{footmisc} %a range of footnote options - noindent
\usepackage[normalem]{ulem} %Gia na kanw underline kapoio text
\usepackage{esvect} %For vector with dot

\renewcommand{\figurename}{Fig.} %Ti leei otan vazw eikones (Fig.1 ...)
\renewcommand{\contentsname}{Table of Contents}
\renewcommand{\chaptername}{Chapter}
\renewcommand{\tablename}{Tab.} %Ti leei otan vazw tables (Capt.1 ...)

%% FOR MATLAB CODE
\usepackage{listings}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}

\renewcommand\bibname{References} %If I don't use it, then instead of the name "References", it will say "Bibliography"

%Package for list of acronym in the end of the document
\usepackage{enumitem}
\newlist{abbrv}{itemize}{1}
\setlist[abbrv,1]{label=,labelwidth=1in,align=parleft,itemsep=0.1\baselineskip,leftmargin=!}

\usepackage{flafter} % Not to let the images and the stuff be presented in the document before their actual reference

\begin{document}
\include{Cover_Master_Thesis_S-Konstantinidou}
\include{Chapter_1}
\include{Chapter_2}
\include{Chapter_3}
\include{Chapter_4}
%\include{Chapter_5}

\newpage
%\chapter*{References}
%\lhead{\emph{References}}
%\label{ref}



\chapter*{List of acronyms}
\addcontentsline{toc}{chapter}{List of acronyms}
\begin{abbrv}
% American Institute of Aeronautics and Astronautics (AIAA)
\item[\textit{ASI}] Agenzia Spaziale Italiana - Italian Space Agency
\item[\textit{CONAE}] Comisión Nacional de Actividades Espaciales of Argentina - \newline Argentinian Space Agency
\item[\textit{DMF}] Debris Mitigation Framework
\item[\textit{ECSS}] European Cooperation for Space Standardization
\item[\textit{EO}] Earth Observation
\item[\textit{EU}] European Union
\item[\textit{GEO}] Geostationary Orbit / Geosynchronous Equatorial Orbit
\item[\textit{GEOSS}] Global Earth Observation System of Systems
\item[\textit{GLAS}] Geoscience Laser Altimeter System
\item[\textit{HRMS}] High Resolution Multi-Spectral
\item[\textit{HSIS}] Hyper Spectral Image Simulator
\item[\textit{IADC}] Inter-Agency Space Debris Coordination Committee
\item[\textit{ISO}] International Organization for Standardization
\item[\textit{ISS}] International Space Station
\item[\textit{LE}] London Economics
\item[\textit{LEO}] Low Earth Orbit
\item[\textit{MELVO}] Moderately Elliptical Very Low Orbit
\item[\textit{MSI}] Multi-Spectral Imager
\item[\textit{MSS}] Multi-Spectral Imaging System
\item[\textit{MSU}] Multi-Spectral Scanner Unit
\item[\textit{MUXCam}] Multi-Spectral Camera
\item[\textit{NIR}] Near Infrared
\item[\textit{ODCWG}] Orbital Debris Co-ordination Working Group
\item[\textit{OECD}] Organization for Economic Co-operation and Development
\item[\textit{PAN}] Panchromatic Imager
\item[\textit{SAR}] Synthetic Aperture Radar
\item[\textit{SIRAL}] SAR Interferometry Radar Altimeter
\item[\textit{SSO}] Sun-Synchronous Orbit
\item[\textit{SSR}] Space Sustainability Rating
\item[\textit{SWIR}] Short-Wave Infrared Light
\item[\textit{UN}] United Nations
\item[\textit{UNCOPUOUS}] United Nations Committee on the Peaceful Uses of Outer Space
\item[\textit{UNOOSA}] United Nations Office for Outer Space Affairs
\item[\textit{VNIR}] Visible and Near-infrared
\item[\textit{WEF}] World Economic Forum
\item[\textit{WFI}] Wide Field Imager
\item[\textit{WPM}] Wide Swath Panchromatic \& Multispectral Camera
\end{abbrv}


\begin{thebibliography}{100}
\bigskip

\bibitem{Cryo2ice_news} Amos J (2020) ESA and NASA line up satellites to measure Antarctic sea-ice. BBC News. Available at: https://www.bbc.com/news/science-environment-53326490 (Accessed July 30, 2020)
\bibitem{Cosmos} Battagliere ML, Daraio MG, Lenti F, Pisani AR, Coletta A (2018) Cosmo-Skymed and the ASO-CONAE cooperation: The SIASGE Programme. 68th International Astronautical Congress (IAC), Bremen, Germany, 1-5 October 2018.
\bibitem{Belward 2015} Belward AS, Skøien JO (2015) Who launched what, when and why; trends in global land-cover observation capacity from civilian earth observation satellites. ISPRS Journal of Photogrammetry and Remote Sensing, May; 103: 115–128.
\bibitem{Blake} Blake JA, Chote P, Pollacco D, Feline W, Privett G, Ash A, Eves S, Greenwood N, Marsh TR, Veras D, Watson C (2020) DebrisWatch I: A survey of faint geosynchronous debris. Advances in Space Research
\bibitem{Amazon} Boyle A (April 4, 2019) Amazon to offer broadband access from orbit with 3,236-satellite ‘Project Kuiper’ constellation. GeekWire. Available at: https://www.geekwire.com/2019/amazon-project-kuiper-broadband-satellite/ (Accessed July 1, 2020)
\bibitem{Braun} Braun V, Lemmens S (2020) Addressing space debris mitigation in satellite mission design. 71st International Astronautical Congress (IAC) – The CyberSpace Edition, 12-14 October 2020
\bibitem{Cadman} Cadman J (May 18, 2020) Op-ed | An unexpected effect: the industry’s recent challenges prove the importance of space. Space News. Available at: https://spacenews.com/op-ed-an-unexpected-effect-the-industrys-recent-challenges-prove-the-importance-of-space/ (Accessed July 1, 2020)
\bibitem{Campbell} Campbell BA, McCandless PW (1996) Introduction to space sciences and spacecraft applications. Elsevier
\bibitem{Committee 2019} Committee on the Peaceful Uses of Outer Space (2019) The “Space2030” Agenda: Space as a driver of sustainable development, Vienna, Report No.: 28th.
\bibitem{Crisp 2020} Crisp NH, Roberts PC, Livadiotti S, Oiko VTA, Edmondson S, Haigh SJ, Huyton C, Sinpetru LA, Smith KL, Worrall SD, Becedas J (2020) The benefits of very low earth orbit for earth observation missions. Progress in Aerospace Sciences, 117, p.100619.
\bibitem{Anti-satellite} David L (Feb 2, 2007) China's Anti-Satellite Test: Worrisome Debris Cloud Circles Earth. SPACE.com [Internet] Available at: https://www.space.com/3415-china-anti-satellite-test-worrisome-debris-cloud-circles-earth.html (Accessed July 1, 2020)
\bibitem{Erwin} Erwin S (May 18, 2020) SpaceX rideshare program putting downward pressure on prices [Internet]. Space News. Available at: https://spacenews.com/spacex-rideshare-program-putting-downward-pressure-on-prices/ (Accessed July 1, 2020)
\bibitem{cooperation} ESA (2020) New space satellite pinpoints industrial methane emissions. Available at: https://www.esa.int/Applications/Observing_the_Earth/Copernicus/Sentinel-5P/New_Space_satellite_pinpoints_industrial_methane_emissions (Accessed October 30, 2020)
\bibitem{ESA EO} ESA Space Solutions (August 11, 2020) Newcomers Earth Observation Guide. Report Version 1.9 Available at: https://business.esa.int/newcomers-earth-observation-guide (Accessed November 1, 2020)
\bibitem{ESA 2020} ESA Space Debris Office - ESOC, (Sep 2020) ESA’s Annual Space Environment Report [Internet]. Report No.: 4.0, p. 88. Available at: https://www.sdo.esoc.esa.int/environment_report/Space_Environment_Report_latest.pdf
%Statistics: https://sdup.esoc.esa.int/discosweb/statistics/
\bibitem{LE_Esteve} Esteve R (2020) Earth Observation: a tool for a more resilient and sustainable world? London Economics: Space In Focus, Issue 2
\bibitem{Space sustainability} Foust J (May 7, 2019) Consortium to develop “space sustainability” rating system. Space News. Available at: https://spacenews.com/consortium-to-develop-space-sustainability-rating-system/ (Accessed July 1, 2020)
\bibitem{Griffin} Griffin M (2010) Orbit/Spectrum Allocation Procedures. Space Services Department ITU Radiocommunication Bureau (BR) Conference of ITU in Bangkok, Thailand
\bibitem{Hallex} Hallex MA, Cottom TS (2020) Proliferated Commercial Satellite Constellations - Implications for National Security. Joint Force Quarterly (JFQ) 97
\bibitem{Kepler} Henry C (August 29, 2018) Kepler Communications opens launch bids for Gen-1 LEO constellation. Space News. Available at: https://spacenews.com/kepler-communications-opens-launch-bids-for-gen-1-leo-constellation/ (Accessed July 2, 2020)
\bibitem{Viasat} Henry C (April 24, 2020) Viasat gets FCC approval for MEO constellation. Space News. Available at: https://spacenews.com/viasat-gets-fcc-approval-for-meo-constellation/ (Accessed July 1, 2020)
\bibitem{IADC 2007} Inter-Agency Space Debris Coordinate Committee (IADC) -  Steering Group and Working Group 4 (2007) IADC Space Debris Mitigation Guidelines. Report No.: 22.4. Revision 1
%Available at: https://www.unoosa.org/documents/pdf/spacelaw/sd/IADC-2002-01-IADC-Space_Debris-Guidelines-Revision1.pdf
\bibitem{Kelso 2009} Kelso TS (2009) Analysis and Implications of the Iridium 33-Cosmos 2251 Collision. InAdvanced Maui Optical and Space Surveillance Technologies Conference
\bibitem{Klinkrad 2006} Klinkrad H (2006) Space Debris: Models and Risk Analysis. Springer Verlag, 1st ed., p.430
\bibitem{Klinkrad 2009} Klinkrad H, Johnson NL (2009) Space debris environment remediation concepts. 5th European Conference on Space Debris. In Darmstadt, Germany; (ESA SP-672). 
\bibitem{Kramer 2002} Kramer H (2002) Observation of the Earth and its Environment. Springer Verlag, 4th ed., p.1514, Updated version: Apr, 2020 Available at: https://directory.eoportal.org/web/eoportal/kramer
\bibitem{Newspace} Kulu E (2020) NewSpace Index - Overview of commercial satellite constellations. [Database] Available at: https://www.newspace.im/
\bibitem{Lapaine} Lapaine M, Usery EL (2017) Choosing a map projection. Cham: Springer
\bibitem{Letizia 2019} Letizia F, Lemmens S, Bastida Virgili B, Krag H. (2019) Application of a debris index for global evaluation of mitigation strategies. Acta Astronautica. 161:348–62.
\bibitem{Luo} Luo X, Wang M, Dai G, Chen X (2017) A novel technique to compute the revisit time of satellites and its application in remote sensing satellite optimization design. International Journal of Aerospace Engineering
\bibitem{Oneweb_bankruptcy} Malik T (March 28, 2020) OneWeb, a satellite internet startup, files for Chapter 11 bankruptcy. SPACE.com [Internet] Available at: https://www.space.com/oneweb-satellite-internet-startup-files-for-bankruptcy.html (Accessed July 1, 2020)
\bibitem{Meseguer} Meseguer J, Pérez-Grande I, Sanz-Andrés A (2012) Keplerian orbits - Spacecraft thermal control. Elsevier p.39-57
\bibitem{Satellogic} Mohney D (January 16, 2019) Satellogic signs launch contracts for 90 imaging satellites. Space It Bridge. Available at: https://www.spaceitbridge.com/satellogic-signs-launch-contracts-for-90-imaging-satellites.htm (Accessed July 1, 2020)
\bibitem{Montenbruck} Montenbruck O, Gill E, Lutze F (2002) Satellite orbits: models, methods, and applications. Appl. Mech. Rev., 55(2), B27-B28
% Source in the pc: ESPACE-TUM > 1st semester > Orbit Mechanics
\bibitem{muranaka} Muranaka T, Okumura T, Ueno K, Otsuka S, Ohkawa Y (2020) Space debris removal using drag force intensifier applying charged membrane: System design and feasibility studies. 71st International Astronautical Congress (IAC) – The CyberSpace Edition, 12-14 October 2020. 
\bibitem{NASA} National Aeronautics and Space Administration (NASA) (2011) USA Space Debris Environment, Operations, and Policy Updates [Internet]. 48th Session of the Scientific and Technical Subcommittee Committee on the Peaceful Uses of Outer Space United Nations. Available from: https://www.unoosa.org/pdf/pres/stsc2011/tech-31.pdf
\bibitem{UNOOSA} Office for Outer Space Affairs (2020) Access to Space for All. Symposium in Vienna International Center - February 2020. Available at: https://www.unoosa.org/oosa/en/ourwork/access2space4all/index.html (Accessed July 30, 2020)
\bibitem{Cryo2ice} Ramsayer K (2020) Syncing NASA Laser, ESA Radar for a New Look at Sea Ice. NASA's Goddard Space Flight Center. Available at: https://www.nasa.gov/feature/goddard/2020/syncing-nasa-laser-esa-radar-for-a-new-look-at-sea-ice (Accessed July 30, 2020)
\bibitem{Value UK} Sadlier G, Flytkjær R, Sabri F, Robin N. (2018) Value of satellite-derived Earth Observation capabilities to the UK Government today and by 2020 - Evidence from nine domestic civil use cases. UK: London Economics (LE).
\bibitem{active} Shan M, Guo J, Gill E (2016) Review and comparison of active space debris capturing and removal methods. Progress in Aerospace Sciences, 80, 18-32.
\bibitem{CNBC} Sheetz M (Jun 9, 2020) How Planet’s new satellite fleet will bring detailed images of places on Earth up to 12 times a day. Investing in Space - CNBC. Available at: https://www.cnbc.com/2020/06/09/planets-skysats-will-take-images-up-to-12-times-a-day-launched-with-help-of-spacex.html (Accessed July 1, 2020)
\bibitem{Somma 2019} Somma GL, Lewis HG, Colombo C (2019) Sensitivity analysis of launch activities in Low Earth Orbit. Acta Astronautica, 158:129–39.
\bibitem{BRICS} Spacewatch Africa (2020) BRICS member states negotiating Earth Observation Satellite sharing framework. Business Intelligence About Space Activities. Available at: https://spacewatch.global/2019/12/brics-member-states-negotiating-earth-observation-satellite-sharing-framework/ (Accessed July 17, 2020)
\bibitem{takeichi} Takeichi N, Tachibana N (2020) A space debris removal strategy using a collision with small relative velocity. 71st International Astronautical Congress (IAC) – The CyberSpace Edition, 12-14 October 2020
\bibitem{pLEO} Taverney T (March 5, 2020) Op-ed | Proliferated LEO is risky but necessary. Space News. Available at: https://spacenews.com/op-ed-proliferated-leo-is-risky-but-necessary/ (Accessed July 1, 2020)
\bibitem{UCS} Union of Concerned Scientists (2020) UCS Satellite Database [Internet]. Published: Dec 8, 2005. Updated: August 1, 2020. Available at: https://www.ucsusa.org/resources/satellite-database (Accessed November 1, 2020)
\bibitem{Undseth} Undseth M, Jolly C, Olivari M (2020) Space sustainability: The economics of space debris in perspective. OECD Science, Technology and Industry Policy Papers, No. 87, OECD Publishing, Paris
\bibitem{UNOOSA} United Nations Office for Outer Space Affairs (2010) Space Debris Mitigation Guidelines of the Committee on the Peaceful Uses of Outer Space. Vienna; Available at: https://www.unoosa.org/pdf/publications/st_space_49E.pdf (Accessed July 30, 2020)
\bibitem{Vallado} Vallado DA (2001) Fundamentals of astrodynamics and applications (Vol. 12) 4th edition. Springer Science \& Business Media
\bibitem{crowded} Wattles J (Oct 9, 2020) Space is becoming too crowded, Rocket Lab CEO warns. CNN Business. Available at: https://edition.cnn.com/2020/10/07/business/rocket-lab-debris-launch-traffic-scn/index.html
\bibitem{NRO} Werner D (Jun 21, 2020) NRO to award multiple imagery contracts by year’s end. Space News. Available at: https://spacenews.com/nro-to-award-multiple-imagery-contracts-by-years-end/ (Accessed July 30, 2020)
\bibitem{Hongyun} Zhao Lei (Dec 2018) China begins space-based broadband project. Jiuquan Satellite Launch Center | chinadaily.com.cn Available at: https://www.chinadaily.com.cn/a/201812/22/WS5c1d82d6a3107d4c3a002337.html (Accessed July 1, 2020)



%The easiest thing in Zotero --> Ctrl + A, right-click, Create bibliography from items, Copy to Clipboard and then, copy paste to all of the \bibitem and the {...} for the citation.

\end{thebibliography}


\newpage
\chapter*{Appendices}
\lhead{\emph{Appendices}}
\label{app}
\addcontentsline{toc}{chapter}{Appendices}

\begin{longtable}{|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|}
    %\centering
    %\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|}
    \hline
        id & international\_designator & name & epoch & inclination & raan & eccentricity & omega & mean\_anomaly & mean\_motion & date\_launched & orbit\_lifetime & sensors & swath\_width & resolution & revisit\_time & type\_of\_sensor & sso \\ \hline
        1 & 2014-016A & SENTINEL-1A & 20263.0419 & 98.1822 & 268.7007 & 0.00013670 & 82.3823 & 277.7536 & 14.5920 & 2014-04-03 & 7.25 & SAR & 80, 250, 400 & 5x5, 5x20, 20x40 & 3.6257 & active & y \\ \hline
        2 & 2015-028A & SENTINEL-2A & 20263.1097 & 98.5684 & 336.0010 & 0.00013050 & 87.6304 & 272.5057 & 14.3081 & 2015-06-23 & 7.25 & MSI & 290 & 10, 20, 60 & 10.0001 & passive & y \\ \hline
        3 & 2016-011A & SENTINEL-3A & 20262.6319 & 98.6306 & 328.0384 & 0.00009010 & 98.1063 & 262.0220 & 14.2673 & 2016-02-16 & 7 & SAR, MWR & 1270 & 300 & 1.1817 & active & y \\ \hline
        4 & 2016-025A & SENTINEL-1B & 20262.8014 & 98.1822 & 268.2887 & 0.00013450 & 80.1540 & 279.9807 & 14.5920 & 2016-04-25 & 7.25 & SAR & 80, 250, 400 & 5x5, 5x20, 20x40 & 3.6257 & active & y \\ \hline
        5 & 2017-013A & SENTINEL-2B & 20263.0747 & 98.5641 & 335.9613 & 0.00010510 & 79.7105 & 280.4178 & 14.3082 & 2017-03-07 & 7.25 & MSI & 290 & 10, 20, 60 & 10.0001 & passive & y \\ \hline
        6 & 2018-039A & SENTINEL-3B & 20263.1656 & 98.6204 & 328.5301 & 0.00007140 & 93.5408 & 266.5854 & 14.2674 & 2018-04-25 & 7 & SAR, MWR & 1270 & 300 & 1.1757 & active & y \\ \hline
        7 & 2017-064A & SENTINEL-5P & 20262.4325 & 98.7398 & 200.3283 & 0.00011530 & 82.0562 & 278.0744 & 14.1954 & 2017-10-13 & 7 & TROPOMI & 2600 & 5500-7000 & 1.1120 & passive & y \\ \hline
        8 & 2016-040H & FLOCK 2P-6 & 20263.1637 & 97.3176 & 324.9911 & 0.00095600 & 191.9994 & 168.1018 & 15.2663 & 2016-06-22 & 3 & VIS, NIR & 80, 100 & 03-May & 3.9984 & passive & y \\ \hline
        9 & 2016-040M & FLOCK 2P-9 & 20263.1129 & 97.3173 & 324.7119 & 0.00099870 & 191.7621 & 168.3386 & 15.2657 & 2016-06-22 & 3 & VIS, NIR & 80, 100 & 03-May & 3.9984 & passive & y \\ \hline
        10 & 2016-040P & FLOCK 2P-10 & 20263.1429 & 97.3222 & 325.6926 & 0.00093310 & 202.4688 & 157.6143 & 15.2668 & 2016-06-22 & 3 & VIS, NIR & 80, 100 & 03-May & 3.9982 & passive & y \\ \hline
        11 & 2016-040Q & FLOCK 2P-8 & 20263.1433 & 97.3217 & 325.4459 & 0.00095070 & 200.8351 & 159.2502 & 15.2657 & 2016-06-22 & 3 & VIS, NIR & 80, 100 & 03-May & 3.9984 & passive & y \\ \hline
        12 & 2016-040R & FLOCK 2P-12 & 20263.1691 & 97.3224 & 325.7685 & 0.00094560 & 202.3159 & 157.7670 & 15.2657 & 2016-06-22 & 3 & VIS, NIR & 80, 100 & 03-May & 3.9984 & passive & y \\ \hline
        13 & 2016-040V & FLOCK 2P-3 & 20263.1209 & 97.3234 & 325.7279 & 0.00092200 & 201.1755 & 158.9104 & 15.2657 & 2016-06-22 & 3 & VIS, NIR & 80, 100 & 03-May & 3.9984 & passive & y \\ \hline
        14 & 2013-066C & SKYSAT-1 & 20263.2665 & 97.6182 & 340.7103 & 0.00204320 & 244.2951 & 115.6162 & 14.9899 & 2013-11-21 & 6 & MSI & 80, 200 & 0.9-2 & 1.0013 & passive & y \\ \hline
        15 & 2014-037D & SKYSAT-2 & 20263.1246 & 98.4641 & 86.5904 & 0.00061790 & 184.1083 & 176.0078 & 14.8131 & 2014-07-08 & 6 & MSI & 80, 200 & 0.9-2 & 4.9986 & passive & y \\ \hline
        16 & 2016-040C & SKYSAT-C1 & 20263.2983 & 97.2190 & 339.5416 & 0.00045910 & 158.0383 & 202.1060 & 15.3782 & 2016-06-22 & 6 & MSI & 80, 200 & 0.9-2 & 9.5001 & passive & y \\ \hline
        17 & 2016-058B & SKYSAT-C4 & 20263.5079 & 97.2017 & 331.9348 & 0.00015150 & 71.0757 & 289.0653 & 15.3795 & 2016-09-16 & 6 & MSI & 80, 200 & 0.9-2 & 8.0028 & passive & y \\ \hline
        18 & 2016-058C & SKYSAT-C5 & 20263.5172 & 97.3499 & 331.4046 & 0.00014910 & 77.4157 & 36.8958 & 15.2408 & 2016-09-16 & 6 & MSI & 80, 200 & 0.9-2 & 12.9997 & passive & y \\ \hline
        19 & 2016-058D & SKYSAT-C2 & 20263.3558 & 97.2021 & 332.1002 & 0.00016220 & 79.1010 & 281.0418 & 15.3802 & 2016-09-16 & 6 & MSI & 80, 200 & 0.9-2 & 8.0025 & passive & y \\ \hline
        20 & 2016-058E & SKYSAT-C3 & 20263.1080 & 97.2018 & 331.8252 & 0.00015530 & 76.8929 & 283.2490 & 15.3801 & 2016-09-16 & 6 & MSI & 80, 200 & 0.9-2 & 8.0025 & passive & y \\ \hline
        21 & 2019-075A & JILIN-01 GAOFEN 2A & 20263.5711 & 97.5031 & 327.1992 & 0.00105000 & 278.5458 & 189.2654 & 15.0931 & 2019-11-13 & 8 & MSI, Video & 40 & 0.75-3 & 11.9998 & passive & y \\ \hline
        22 & 2019-086A & JILIN-01 GAOFEN 2B & 20263.5383 & 97.5033 & 327.6944 & 0.00114960 & 14.7798 & 96.3830 & 15.0931 & 2019-12-07 & 8 & MSI, Video & 40 & 0.75-3 & 11.9998 & passive & y \\ \hline
        23 & 2020-003A & JILIN-01 KUANFU 01 & 20263.4955 & 97.3082 & 327.7176 & 0.00141700 & 108.2787 & 251.9995 & 15.2733 & 2020-01-15 & 8 & MSI, Video & 136 & 4 & 18.9997 & passive & y \\ \hline
        24 & 2020-065A & JILIN-01 GAOFEN 3B & 20263.4973 & 97.5390 & 319.0825 & 0.00116840 & 267.7610 & 204.6344 & 15.0890 & 2020-09-15 & 8 & MSI, Video & 17, 40, 100 & 01-Apr & 12.9978 & passive & y \\ \hline
        25 & 2020-065B & JILIN-01 GAOFEN 3C & 20263.4955 & 97.5339 & 319.0807 & 0.00111800 & 277.2968 & 190.6076 & 15.0924 & 2020-09-15 & 8 & MSI, Video & 17, 40, 100 & 01-Apr & 12.0004 & passive & y \\ \hline
        26 & 2020-065C & JILIN-01 GAOFEN 3D & 20263.4954 & 97.5431 & 319.0860 & 0.00111780 & 276.7852 & 191.2065 & 15.0926 & 2020-09-15 & 8 & MSI, Video & 17, 40, 100 & 01-Apr & 12.0001 & passive & y \\ \hline
        27 & 2020-065D & JILIN-01 GAOFEN 3E & 20263.4953 & 97.5387 & 319.0836 & 0.00108060 & 278.8205 & 189.2211 & 15.0929 & 2020-09-15 & 8 & MSI, Video & 17, 40, 100 & 01-Apr & 11.9999 & passive & y \\ \hline
        28 & 2020-065E & JILIN-01 GAOFEN 3F & 20263.4949 & 97.5322 & 319.0808 & 0.00121450 & 279.8738 & 188.2449 & 15.0945 & 2020-09-15 & 8 & MSI, Video & 17, 40, 100 & 01-Apr & 11.9987 & passive & y \\ \hline
        29 & 2020-065F & JILIN-01 GAOFEN 3G & 20263.4948 & 97.5444 & 319.0872 & 0.00123240 & 279.7616 & 188.3282 & 15.0947 & 2020-09-15 & 8 & MSI, Video & 17, 40, 100 & 01-Apr & 11.9986 & passive & y \\ \hline
        30 & 2020-065G & JILIN-01 GAOFEN 3H & 20263.4988 & 97.5336 & 319.0852 & 0.00128700 & 278.9376 & 211.1886 & 15.0950 & 2020-09-15 & 8 & MSI, Video & 17, 40, 100 & 01-Apr & 11.9983 & passive & y \\ \hline
        31 & 2020-065H & JILIN-01 GAOFEN 3I & 20263.4947 & 97.5421 & 319.0859 & 0.00130010 & 278.8338 & 189.3484 & 15.0951 & 2020-09-15 & 8 & MSI, Video & 17, 40, 100 & 01-Apr & 11.9983 & passive & y \\ \hline
        32 & 2020-065J & JILIN-01 GAOFEN 3J & 20263.4945 & 97.5374 & 319.0837 & 0.00134560 & 280.0072 & 188.5745 & 15.0962 & 2020-09-15 & 8 & MSI, Video & 17, 40, 100 & 01-Apr & 11.9999 & passive & y \\ \hline
        33 & 2018-099BG & BLACKSKY GLOBAL 2 & 20263.3521 & 97.6958 & 333.4278 & 0.00122740 & 234.2037 & 125.8044 & 14.9555 & 2018-12-03 & 3 & MSI & 30, 100 & 0.9-1.1 & 19.0014 & passive & y \\ \hline
        35 & 2017-008C & FLOCK 3P-20 & 20285.9038 & 97.3529 & 351.5936 & 0.00074090 & 237.2433 & 122.8092 & 15.2651 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9986 & passive & y \\ \hline
        36 & 2017-008D & FLOCK 3P-8 & 20285.7480 & 97.3531 & 351.5410 & 0.00065790 & 236.9688 & 123.0919 & 15.2663 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        37 & 2017-008E & FLOCK 3P-51 & 20285.8511 & 97.3534 & 351.8093 & 0.00060930 & 258.1600 & 101.8955 & 15.2665 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        38 & 2017-008J & FLOCK 3P-24 & 20285.7686 & 97.3534 & 353.5999 & 0.00066550 & 220.4602 & 139.6143 & 15.2858 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 18.0022 & passive & y \\ \hline
        39 & 2017-008T & FLOCK 3P-4 & 20285.7522 & 97.3530 & 351.5293 & 0.00066210 & 235.7762 & 124.2850 & 15.2665 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        40 & 2017-008U & FLOCK 3P-2 & 20285.6249 & 97.3544 & 351.4924 & 0.00064370 & 232.3855 & 127.6800 & 15.2667 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        41 & 2017-008W & FLOCK 3P-3 & 20286.1796 & 97.3539 & 352.1964 & 0.00065390 & 230.2570 & 129.8094 & 15.2716 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 19.0017 & passive & y \\ \hline
        42 & 2017-008AA & FLOCK 3P-12 & 20285.7434 & 97.3547 & 351.6535 & 0.00062820 & 238.1394 & 121.9234 & 15.2663 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        43 & 2017-008AD & FLOCK 3P-11 & 20286.1435 & 97.3534 & 352.0116 & 0.00065390 & 234.5957 & 125.4671 & 15.2662 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        44 & 2017-008AE & FLOCK 3P-60 & 20285.7877 & 97.3553 & 351.8482 & 0.00059770 & 237.6152 & 122.4509 & 15.2666 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        45 & 2017-008AF & FLOCK 3P-58 & 20286.1407 & 97.3543 & 352.0456 & 0.00063360 & 236.4626 & 123.6008 & 15.2664 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        46 & 2017-008AG & FLOCK 3P-57 & 20285.7306 & 97.3537 & 351.6617 & 0.00063940 & 235.4257 & 124.6379 & 15.2664 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        47 & 2017-008AJ & FLOCK 3P-70 & 20285.6679 & 97.3578 & 352.0728 & 0.00063760 & 240.2498 & 119.8107 & 15.2661 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        48 & 2017-008AP & FLOCK 3P-86 & 20285.6597 & 97.3575 & 352.0836 & 0.00058460 & 241.3603 & 118.7049 & 15.2662 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        49 & 2017-008AS & FLOCK 3P-34 & 20285.7301 & 97.3556 & 351.7456 & 0.00059800 & 235.0120 & 125.0558 & 15.2663 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        50 & 2017-008AU & FLOCK 3P-33 & 20285.8530 & 97.3547 & 351.7129 & 0.00058680 & 238.0301 & 122.0368 & 15.2627 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9992 & passive & y \\ \hline
        51 & 2017-008BF & FLOCK 3P-49 & 20285.7437 & 97.3544 & 351.8560 & 0.00061080 & 258.6262 & 101.4291 & 15.2680 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9979 & passive & y \\ \hline
        52 & 2017-008BH & FLOCK 3P-68 & 20286.1731 & 97.3538 & 352.1302 & 0.00063490 & 255.9040 & 104.1493 & 15.2667 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        53 & 2017-008BP & FLOCK 3P-61 & 20285.7692 & 97.3540 & 351.7887 & 0.00057770 & 262.4278 & 97.6305 & 15.2665 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        54 & 2017-008BQ & FLOCK 3P-40 & 20286.1568 & 97.3534 & 352.0634 & 0.00058170 & 264.6730 & 95.3845 & 15.2664 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        55 & 2017-008BU & FLOCK 3P-54 & 20285.7577 & 97.3550 & 351.7693 & 0.00053020 & 266.6288 & 93.4345 & 15.2664 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        56 & 2017-008BY & FLOCK 3P-23 & 20285.7588 & 97.3539 & 351.5035 & 0.00067520 & 233.4981 & 126.5637 & 15.2666 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        57 & 2017-008BZ & FLOCK 3P-76 & 20285.8668 & 97.3584 & 352.3372 & 0.00064820 & 241.2511 & 118.8077 & 15.2661 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        58 & 2017-008CD & FLOCK 3P-32 & 20285.7204 & 97.3540 & 351.6817 & 0.00062250 & 235.2041 & 124.8612 & 15.2669 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        59 & 2017-008CF & FLOCK 3P-77 & 20285.7831 & 97.3566 & 352.1925 & 0.00062900 & 241.8518 & 118.2085 & 15.2664 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        60 & 2017-008CG & FLOCK 3P-80 & 20285.7645 & 97.3568 & 352.2000 & 0.00059150 & 242.8406 & 117.2230 & 15.2669 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        61 & 2017-008CH & FLOCK 3P-66 & 20285.7787 & 97.3544 & 351.8045 & 0.00062930 & 256.8065 & 103.2472 & 15.2667 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        62 & 2017-008CJ & FLOCK 3P-65 & 20285.7774 & 97.3553 & 351.8580 & 0.00061010 & 256.9262 & 103.1296 & 15.2668 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        63 & 2017-008CK & FLOCK 3P-50 & 20285.9051 & 97.3559 & 352.0504 & 0.00057760 & 258.1523 & 101.9068 & 15.2666 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        64 & 2017-008CM & FLOCK 3P-46 & 20285.9031 & 97.3538 & 351.8572 & 0.00057540 & 258.5700 & 101.4893 & 15.2665 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        65 & 2017-008CN & FLOCK 3P-47 & 20285.9036 & 97.3538 & 351.8610 & 0.00057900 & 259.1747 & 100.8840 & 15.2666 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        66 & 2017-008CQ & FLOCK 3P-64 & 20286.1584 & 97.3534 & 352.1129 & 0.00057680 & 263.3122 & 96.7461 & 15.2666 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        67 & 2017-008CX & FLOCK 3P-55 & 20286.1227 & 97.3537 & 352.1594 & 0.00052980 & 267.9219 & 92.1413 & 15.2666 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9982 & passive & y \\ \hline
        68 & 2017-008CZ & FLOCK 3P-81 & 20285.8687 & 97.3571 & 352.2374 & 0.00063420 & 242.9910 & 117.0682 & 15.2652 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9986 & passive & y \\ \hline
        69 & 2017-008DA & FLOCK 3P-87 & 20286.1486 & 97.3558 & 352.3558 & 0.00063730 & 238.5145 & 121.5472 & 15.2644 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9989 & passive & y \\ \hline
        70 & 2017-008DE & FLOCK 3P-74 & 20285.7438 & 97.3578 & 352.1564 & 0.00065550 & 239.5468 & 120.5124 & 15.2662 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        71 & 2017-008DF & FLOCK 3P-31 & 20286.1311 & 97.3539 & 352.0451 & 0.00061790 & 234.7602 & 125.3059 & 15.2665 & 2017-02-15 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9983 & passive & y \\ \hline
        72 & 2017-042AB & FLOCK 2K-03 & 20285.8765 & 96.8770 & 147.1136 & 0.00073280 & 271.7313 & 88.3096 & 15.4221 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 16.9999 & passive & y \\ \hline
        73 & 2017-042AC & FLOCK 2K-04 & 20285.8357 & 96.8757 & 147.5522 & 0.00070710 & 271.9129 & 88.1310 & 15.4244 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 16.9972 & passive & y \\ \hline
        74 & 2017-042AH & FLOCK 2K-45 & 20285.8729 & 96.8765 & 147.0919 & 0.00067430 & 267.3861 & 92.6615 & 15.4215 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0004 & passive & y \\ \hline
        75 & 2017-042AL & FLOCK 2K-23 & 20285.5681 & 96.8764 & 147.0018 & 0.00066600 & 269.3112 & 90.7374 & 15.4273 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.9997 & passive & y \\ \hline
        76 & 2017-042AM & FLOCK 2K-21 & 20285.8700 & 96.8777 & 147.1955 & 0.00069140 & 268.7770 & 91.2686 & 15.4217 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0005 & passive & y \\ \hline
        77 & 2017-042AP & FLOCK 2K-07 & 20285.8649 & 96.8778 & 147.2469 & 0.00071840 & 268.8548 & 91.1878 & 15.4223 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 16.9996 & passive & y \\ \hline
        78 & 2017-042AS & FLOCK 2K-40 & 20285.8676 & 96.8776 & 147.2391 & 0.00071570 & 270.0666 & 89.9763 & 15.4216 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0005 & passive & y \\ \hline
        79 & 2017-042AT & FLOCK 2K-39 & 20285.8628 & 96.8776 & 147.2128 & 0.00071080 & 269.5516 & 90.4918 & 15.4217 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0001 & passive & y \\ \hline
        80 & 2017-042AU & FLOCK 2K-37 & 20285.9253 & 96.8769 & 147.2588 & 0.00072120 & 269.9801 & 90.0621 & 15.4218 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0001 & passive & y \\ \hline
        81 & 2017-042AW & FLOCK 2K-31 & 20285.8534 & 96.8767 & 147.1676 & 0.00071150 & 264.2285 & 95.8153 & 15.4220 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 16.9999 & passive & y \\ \hline
        82 & 2017-042AX & FLOCK 2K-32 & 20285.8510 & 96.8771 & 147.1665 & 0.00070760 & 265.4609 & 94.5831 & 15.4218 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0001 & passive & y \\ \hline
        83 & 2017-042AY & FLOCK 2K-29 & 20285.6540 & 96.8771 & 147.0200 & 0.00073590 & 265.1596 & 94.8813 & 15.4216 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0003 & passive & y \\ \hline
        84 & 2017-042AZ & FLOCK 2K-30 & 20285.8463 & 96.8780 & 147.2514 & 0.00073700 & 265.6458 & 94.3949 & 15.4216 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0005 & passive & y \\ \hline
        85 & 2017-042BA & FLOCK 2K-44 & 20285.8429 & 96.8766 & 147.1645 & 0.00080840 & 252.4226 & 107.6140 & 15.4217 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0005 & passive & y \\ \hline
        86 & 2017-042BB & FLOCK 2K-43 & 20285.8511 & 96.8784 & 142.4737 & 0.00101210 & 278.8345 & 81.1755 & 15.3726 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.0007 & passive & y \\ \hline
        87 & 2017-042BC & FLOCK 2K-41 & 20285.8883 & 96.8777 & 147.3400 & 0.00083620 & 254.7394 & 105.2930 & 15.4221 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 16.9999 & passive & y \\ \hline
        88 & 2017-042BE & FLOCK 2K-35 & 20286.1000 & 96.8777 & 147.5080 & 0.00083760 & 253.3905 & 106.6424 & 15.4217 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0006 & passive & y \\ \hline
        89 & 2017-042BM & FLOCK 2K-25 & 20285.9025 & 96.8770 & 147.2768 & 0.00082380 & 254.0362 & 105.9979 & 15.4216 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0009 & passive & y \\ \hline
        90 & 2017-042BP & FLOCK 2K-19 & 20285.8994 & 96.8776 & 147.3332 & 0.00087720 & 255.0761 & 104.9517 & 15.4213 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0007 & passive & y \\ \hline
        91 & 2017-042BQ & FLOCK 2K-18 & 20286.1519 & 96.8776 & 147.5833 & 0.00089130 & 252.4812 & 107.5462 & 15.4207 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0002 & passive & y \\ \hline
        92 & 2017-042BS & FLOCK 2K-16 & 20285.8318 & 96.8784 & 147.3175 & 0.00083900 & 252.2844 & 107.7489 & 15.4211 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 16.9999 & passive & y \\ \hline
        93 & 2017-042BT & FLOCK 2K-15 & 20285.8863 & 96.8782 & 147.4622 & 0.00088500 & 253.3807 & 106.6470 & 15.4212 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 16.9998 & passive & y \\ \hline
        94 & 2017-042BW & FLOCK 2K-12 & 20285.8814 & 96.8776 & 147.3866 & 0.00088220 & 253.2977 & 106.7303 & 15.4214 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0002 & passive & y \\ \hline
        95 & 2017-042BY & FLOCK 2K-10 & 20285.8845 & 96.8772 & 147.2921 & 0.00088390 & 250.5485 & 109.4809 & 15.4212 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0004 & passive & y \\ \hline
        96 & 2017-042BZ & FLOCK 2K-09 & 20285.8767 & 96.8749 & 148.3496 & 0.00083220 & 245.3123 & 114.7261 & 15.4332 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 18.9975 & passive & y \\ \hline
        97 & 2017-042CA & FLOCK 2K-06 & 20286.1153 & 96.8771 & 147.4444 & 0.00073010 & 266.8612 & 93.1801 & 15.4220 & 2017-07-14 & 3 & VIS, NIR & 25, 100 & 3.7 & 16.9999 & passive & y \\ \hline
        98 & 2017-068L & FLOCK 3M-4 & 20287.0404 & 97.4268 & 34.5546 & 0.00167210 & 63.1642 & 297.1301 & 15.2165 & 2017-10-31 & 3 & VIS, NIR & 25, 100 & 3.7 & 4.9979 & passive & y \\ \hline
        99 & 2017-068M & FLOCK 3M-2 & 20286.8719 & 97.4129 & 32.8781 & 0.00153040 & 60.0125 & 300.2628 & 15.2167 & 2017-10-31 & 3 & VIS, NIR & 25, 100 & 3.7 & 4.9978 & passive & y \\ \hline
        100 & 2018-004J & FLOCK 3P-3 & 20286.8686 & 97.4409 & 356.6727 & 0.00101630 & 10.6003 & 349.5446 & 15.2357 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9979 & passive & y \\ \hline
        101 & 2018-004K & FLOCK 3P-2 & 20287.1283 & 97.4413 & 356.8104 & 0.00100940 & 10.1978 & 349.9462 & 15.2336 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9990 & passive & y \\ \hline
        102 & 2018-004M & FLOCK 3P-4 & 20286.8641 & 97.4423 & 356.6178 & 0.00100730 & 13.1266 & 347.0231 & 15.2336 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9990 & passive & y \\ \hline
        103 & 2018-096E & FLOCK 3R-9 & 20287.2062 & 97.4118 & 1.2433 & 0.00182110 & 68.6010 & 346.3902 & 15.2936 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0009 & passive & y \\ \hline
        104 & 2018-096F & FLOCK 3R-12 & 20286.8561 & 97.4139 & 0.9339 & 0.00183070 & 70.6797 & 289.6421 & 15.2937 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0008 & passive & y \\ \hline
        105 & 2018-096G & FLOCK 3R-11 & 20286.7776 & 97.4132 & 0.8698 & 0.00183350 & 70.9455 & 289.3769 & 15.2936 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0008 & passive & y \\ \hline
        106 & 2018-096J & FLOCK 3R-8 & 20286.4312 & 97.4144 & 0.6621 & 0.00188300 & 73.0281 & 287.3021 & 15.2935 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0010 & passive & y \\ \hline
        107 & 2018-096Q & FLOCK 3R-4 & 20287.1235 & 97.4134 & 1.4487 & 0.00215850 & 71.9464 & 351.5784 & 15.2935 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0010 & passive & y \\ \hline
        108 & 2018-096R & FLOCK 3R-3 & 20287.1552 & 97.4119 & 1.5519 & 0.00217960 & 71.2799 & 345.9981 & 15.2937 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0008 & passive & y \\ \hline
        109 & 2018-096T & FLOCK 3R-15 & 20287.1594 & 97.4148 & 1.3786 & 0.00227910 & 73.6303 & 286.7440 & 15.2869 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 18.0008 & passive & y \\ \hline
        110 & 2018-096X & FLOCK 3R-10 & 20287.1243 & 97.4134 & 1.1818 & 0.00181150 & 69.0356 & 291.2821 & 15.2936 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0008 & passive & y \\ \hline
        111 & 2018-096Y & FLOCK 3R-6 & 20287.1737 & 97.4114 & 1.3305 & 0.00187060 & 69.9573 & 344.6758 & 15.2936 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0009 & passive & y \\ \hline
        112 & 2018-096Z & FLOCK 3R-7 & 20287.1671 & 97.4148 & 1.3407 & 0.00187860 & 68.8289 & 345.3730 & 15.2936 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0009 & passive & y \\ \hline
        113 & 2018-096AE & FLOCK 3R-1 & 20287.1384 & 97.4147 & 1.5437 & 0.00219400 & 72.4124 & 287.9511 & 15.2936 & 2018-01-12 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0009 & passive & y \\ \hline
        114 & 2018-099M & FLOCK 3S-1 & 20286.8461 & 97.6923 & 355.7391 & 0.00148090 & 158.1323 & 202.0533 & 14.9504 & 2018-12-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.0000 & passive & y \\ \hline
        115 & 2018-099AG & FLOCK 3S-3 & 20286.9108 & 97.6977 & 356.6624 & 0.00155550 & 154.9523 & 205.2455 & 14.9547 & 2018-12-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 17.9989 & passive & y \\ \hline
        116 & 2018-099BR & FLOCK 3S-2 & 20286.7496 & 97.6968 & 356.6470 & 0.00150040 & 153.5283 & 206.6708 & 14.9567 & 2018-12-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 19.0000 & passive & y \\ \hline
        117 & 2018-111T & FLOCK 3K-4 & 20286.7394 & 97.2528 & 183.3518 & 0.00244320 & 92.4651 & 267.9385 & 15.2600 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 4.0000 & passive & y \\ \hline
        118 & 2018-111U & FLOCK 3K-1 & 20286.7333 & 97.2521 & 183.3115 & 0.00244520 & 92.3271 & 268.0768 & 15.2602 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9999 & passive & y \\ \hline
        119 & 2018-111V & FLOCK 3K-2 & 20286.8585 & 97.2523 & 183.4740 & 0.00248340 & 91.8727 & 268.5356 & 15.2603 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9999 & passive & y \\ \hline
        120 & 2018-111W & FLOCK 3K-6 & 20286.7869 & 97.2530 & 183.4180 & 0.00230350 & 89.3387 & 271.0491 & 15.2604 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9999 & passive & y \\ \hline
        121 & 2018-111Z & FLOCK 3K-5 & 20286.8464 & 97.2527 & 183.5113 & 0.00233030 & 88.3147 & 272.0761 & 15.2608 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9998 & passive & y \\ \hline
        122 & 2018-111AB & FLOCK 3K-8 & 20286.8400 & 97.2520 & 183.4669 & 0.00234430 & 88.6981 & 271.6943 & 15.2612 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9997 & passive & y \\ \hline
        123 & 2018-111AC & FLOCK 3K-7 & 20286.8334 & 97.2527 & 183.4941 & 0.00234650 & 87.9943 & 272.3983 & 15.2614 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9996 & passive & y \\ \hline
        124 & 2018-111AE & FLOCK 3K-11 & 20286.7549 & 97.2528 & 183.4696 & 0.00229450 & 87.4278 & 272.9587 & 15.2615 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9996 & passive & y \\ \hline
        125 & 2018-111AF & FLOCK 3K-10 & 20286.6832 & 97.2527 & 183.4158 & 0.00226890 & 87.2916 & 273.0919 & 15.2619 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9995 & passive & y \\ \hline
        126 & 2018-111AG & FLOCK 3K-9 & 20286.9580 & 97.2522 & 183.6396 & 0.00231130 & 86.8377 & 273.5506 & 15.2613 & 2018-12-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 3.9996 & passive & y \\ \hline
        127 & 2019-018B & FLOCK 4A-1 & 20287.1490 & 97.3970 & 346.1214 & 0.00140880 & 108.6583 & 251.6185 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        128 & 2019-018C & FLOCK 4A-2 & 20287.1107 & 97.3972 & 346.0461 & 0.00143210 & 109.4289 & 250.8497 & 15.2318 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 9.0001 & passive & y \\ \hline
        129 & 2019-018D & FLOCK 4A-3 & 20287.1553 & 97.3965 & 346.1228 & 0.00143930 & 110.3008 & 249.9777 & 15.2326 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        130 & 2019-018L & FLOCK 4A-17 & 20287.9265 & 97.3976 & 347.1344 & 0.00149770 & 112.6513 & 247.6309 & 15.2326 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        131 & 2019-018M & FLOCK 4A-18 & 20287.9303 & 97.3977 & 347.1409 & 0.00149970 & 113.2972 & 246.9845 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        132 & 2019-018N & FLOCK 4A-19 & 20287.8964 & 97.3975 & 347.1694 & 0.00148580 & 113.8850 & 246.3945 & 15.2328 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9995 & passive & y \\ \hline
        133 & 2019-018R & FLOCK 4A-7 & 20287.7568 & 97.3986 & 347.1162 & 0.00125670 & 116.8406 & 243.4117 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        134 & 2019-018S & FLOCK 4A-6 & 20288.1586 & 97.3965 & 347.4975 & 0.00122860 & 116.4949 & 327.8231 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        135 & 2019-018T & FLOCK 4A-5 & 20287.9192 & 97.3983 & 347.3315 & 0.00127280 & 117.9141 & 242.3386 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        136 & 2019-018U & FLOCK 4A-11 & 20287.9116 & 97.3984 & 347.3427 & 0.00127240 & 119.1878 & 241.0633 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        137 & 2019-018V & FLOCK 4A-10 & 20287.9810 & 97.3982 & 347.3842 & 0.00128440 & 119.8827 & 240.3688 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        138 & 2019-018W & FLOCK 4A-9 & 20287.9075 & 97.3985 & 347.3548 & 0.00128630 & 121.2000 & 239.0499 & 15.2327 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9996 & passive & y \\ \hline
        139 & 2019-018X & FLOCK 4A-16 & 20287.9039 & 97.3979 & 347.3191 & 0.00129980 & 121.5672 & 238.6835 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        140 & 2019-018Y & FLOCK 4A-15 & 20287.8846 & 97.3980 & 347.3483 & 0.00131180 & 122.8786 & 237.3715 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        141 & 2019-018AA & FLOCK 4A-13 & 20287.9579 & 97.3982 & 347.3797 & 0.00136190 & 123.9545 & 236.2988 & 15.2326 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9996 & passive & y \\ \hline
        142 & 2019-018AE & FLOCK 4A-12 & 20288.1411 & 97.3963 & 347.5026 & 0.00122810 & 117.4844 & 294.5989 & 15.2325 & 2019-04-01 & 3 & VIS, NIR & 25, 100 & 3.7 & 8.9997 & passive & y \\ \hline
        143 & 2019-081E & FLOCK 4P-10 & 20287.2100 & 97.4833 & 347.2776 & 0.00130650 & 201.2870 & 158.7823 & 15.2015 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 9.9974 & passive & y \\ \hline
        144 & 2019-081F & FLOCK 4P-11 & 20287.3307 & 97.4831 & 347.4119 & 0.00129860 & 201.4331 & 158.6361 & 15.2020 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 9.9989 & passive & y \\ \hline
        145 & 2019-081G & FLOCK 4P-12 & 20287.7856 & 97.4832 & 347.8874 & 0.00126960 & 199.6654 & 160.4093 & 15.2023 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 5.0024 & passive & y \\ \hline
        146 & 2019-081H & FLOCK 4P-4 & 20287.7623 & 97.4853 & 347.9696 & 0.00121740 & 188.9383 & 171.1637 & 15.2025 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 5.0022 & passive & y \\ \hline
        147 & 2019-081J & FLOCK 4P-3 & 20287.2303 & 97.4855 & 347.4530 & 0.00119770 & 190.6319 & 169.4665 & 15.2027 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 5.0022 & passive & y \\ \hline
        148 & 2019-081K & FLOCK 4P-2 & 20287.7735 & 97.4842 & 347.9339 & 0.00117740 & 189.1643 & 170.9379 & 15.2017 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 5.0025 & passive & y \\ \hline
        149 & 2019-081L & FLOCK 4P-1 & 20287.7681 & 97.4841 & 347.9389 & 0.00116320 & 189.1115 & 170.9910 & 15.2021 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 5.0024 & passive & y \\ \hline
        150 & 2019-081N & FLOCK 4P-7 & 20287.4208 & 97.4843 & 347.6314 & 0.00110910 & 191.3806 & 168.7180 & 15.2019 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 5.0069 & passive & y \\ \hline
        151 & 2019-081P & FLOCK 4P-6 & 20287.7173 & 97.4838 & 347.9924 & 0.00108590 & 190.8276 & 169.2727 & 15.2034 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 5.0021 & passive & y \\ \hline
        152 & 2019-081Q & FLOCK 4P-5 & 20287.6005 & 97.4842 & 347.8515 & 0.00106710 & 192.0614 & 168.0367 & 15.2021 & 2019-11-27 & 3 & VIS, NIR & 25, 100 & 3.7 & 5.0024 & passive & y \\ \hline
        153 & 2020-061L & FLOCK 4V-9 & 20287.7700 & 97.5156 & 0.1290 & 0.00033860 & 182.0120 & 178.1096 & 15.0987 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.0012 & passive & y \\ \hline
        154 & 2020-061M & FLOCK 4V-12 & 20287.7693 & 97.5157 & 0.1306 & 0.00034990 & 181.0479 & 179.0744 & 15.0990 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.0010 & passive & y \\ \hline
        155 & 2020-061P & FLOCK 4V-11 & 20287.7689 & 97.5158 & 0.1323 & 0.00034250 & 178.5286 & 181.5954 & 15.0991 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.0010 & passive & y \\ \hline
        156 & 2020-061Q & FLOCK 4V-14 & 20287.1720 & 97.5158 & 359.5475 & 0.00033190 & 180.3135 & 179.8093 & 15.0993 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.0008 & passive & y \\ \hline
        157 & 2020-061S & FLOCK 4V-8 & 20287.1708 & 97.5157 & 359.5483 & 0.00021080 & 185.0527 & 175.0682 & 15.0998 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.0004 & passive & y \\ \hline
        158 & 2020-061T & FLOCK 4V-6 & 20287.1698 & 97.5158 & 359.5505 & 0.00021710 & 180.4881 & 179.6346 & 15.1001 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.0003 & passive & y \\ \hline
        159 & 2020-061U & FLOCK 4V-5 & 20287.1695 & 97.5156 & 359.5498 & 0.00021120 & 180.5608 & 179.5619 & 15.1003 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.0001 & passive & y \\ \hline
        160 & 2020-061V & FLOCK 4V-7 & 20287.1693 & 97.5158 & 359.5513 & 0.00020240 & 179.7264 & 180.3967 & 15.1003 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 11.0001 & passive & y \\ \hline
        161 & 2020-061AA & FLOCK 4V-10 & 20287.7539 & 97.5160 & 0.1527 & 0.00020850 & 118.5150 & 241.6290 & 15.1047 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 9.0089 & passive & y \\ \hline
        162 & 2020-061AB & FLOCK 4V-13 & 20287.7530 & 97.5158 & 0.1535 & 0.00021770 & 116.6400 & 243.5053 & 15.1050 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 9.0198 & passive & y \\ \hline
        163 & 2020-061AT & FLOCK 4V-1 & 20287.4797 & 97.5158 & 359.9039 & 0.00045180 & 121.6898 & 238.4773 & 15.1083 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 10.0008 & passive & y \\ \hline
        164 & 2020-061AU & FLOCK 4V-4 & 20287.4778 & 97.5156 & 359.9058 & 0.00047030 & 119.0885 & 241.0816 & 15.1089 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 10.0004 & passive & y \\ \hline
        165 & 2020-061BB & FLOCK 4V-2 & 20287.4798 & 97.5159 & 359.9047 & 0.00045160 & 121.5325 & 238.6346 & 15.1081 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 10.0010 & passive & y \\ \hline
        166 & 2020-061BC & FLOCK 4V-3 & 20287.4786 & 97.5157 & 359.9050 & 0.00046160 & 119.8250 & 240.3439 & 15.1086 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 10.0006 & passive & y \\ \hline
        167 & 2020-061BD & FLOCK 4V-16 & 20287.4348 & 97.4678 & 359.8040 & 0.00105990 & 88.0999 & 272.1447 & 15.1454 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 14.9976 & passive & y \\ \hline
        168 & 2020-061BE & FLOCK 4V-15 & 20287.2862 & 97.4635 & 359.6918 & 0.00045780 & 112.2008 & 247.9711 & 15.1606 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 10.0054 & passive & y \\ \hline
        169 & 2020-061BF & FLOCK 4V-17 & 20287.7527 & 97.4606 & 0.1391 & 0.00048010 & 100.1722 & 260.0052 & 15.1590 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 10.0022 & passive & y \\ \hline
        170 & 2020-061BG & FLOCK 4V-18 & 20287.8921 & 97.4712 & 0.2617 & 0.00091760 & 88.4163 & 271.8120 & 15.1485 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 7.0018 & passive & y \\ \hline
        171 & 2020-061BH & FLOCK 4V-19 & 20288.0206 & 97.4592 & 0.3978 & 0.00053110 & 84.1563 & 276.0275 & 15.1579 & 2020-09-03 & 3 & VIS, NIR & 25, 100 & 3.7 & 6.9976 & passive & y \\ \hline
        172 & 2020-067A & HUANJING 2A & 20293.1416 & 98.0463 & 8.3282 & 0.00183320 & 297.8411 & 62.0953 & 14.7572 & 2020-09-27 & 3 & VIS, NIR & 700 & 16, 48 & 4.0005 & passive & y \\ \hline
        173 & 2020-067B & HUANJING 2B & 20293.1259 & 98.0478 & 8.3520 & 0.00239010 & 302.7154 & 57.1765 & 14.7691 & 2020-09-27 & 3 & VIS, NIR & 700 & 16, 48 & 4.2511 & passive & y \\ \hline
        174 & 2017-068F & SKYSAT-C6 & 20301.8451 & 97.2489 & 54.7572 & 0.00014360 & 159.1771 & 200.9534 & 15.3862 & 2017-10-31 & 6 & MSI & 80, 200 & 0.5 & 7.9994 & passive & y \\ \hline
        176 & 2017-068E & SKYSAT-C7 & 20301.8553 & 97.2473 & 54.5328 & 0.00014730 & 85.3486 & 274.7928 & 15.3862 & 2017-10-31 & 6 & MSI & 80, 200 & 0.5 & 7.9994 & passive & y \\ \hline
        177 & 2017-068D & SKYSAT-C8 & 20301.8678 & 97.2468 & 54.5360 & 0.00013760 & 350.0745 & 10.0473 & 15.3853 & 2017-10-31 & 6 & MSI & 80, 200 & 0.5 & 7.9999 & passive & y \\ \hline
        178 & 2017-068C & SKYSAT-C9 & 20301.8736 & 97.2426 & 53.7107 & 0.00022180 & 126.0889 & 234.0562 & 15.3860 & 2017-10-31 & 6 & MSI & 80, 200 & 0.5 & 7.9994 & passive & y \\ \hline
        179 & 2017-068B & SKYSAT-C10 & 20301.8860 & 97.2469 & 54.1782 & 0.00030290 & 5.5568 & 354.5711 & 15.3861 & 2017-10-31 & 6 & MSI & 80, 200 & 0.5 & 7.9994 & passive & y \\ \hline
        180 & 2017-068A & SKYSAT-C11 & 20301.8979 & 97.2428 & 54.3373 & 0.00083740 & 298.3219 & 61.7182 & 15.3857 & 2017-10-31 & 6 & MSI & 80, 200 & 0.5 & 7.9997 & passive & y \\ \hline
        181 & 2018-099AR & SKYSAT-C12 & 20301.9110 & 97.2028 & 10.6366 & 0.00020500 & 126.6304 & 233.5130 & 15.3807 & 2018-12-03 & 6 & MSI & 80, 200 & 0.5 & 8.0022 & passive & y \\ \hline
        182 & 2018-099AW & SKYSAT-C13 & 20301.7820 & 97.2343 & 10.4662 & 0.00027160 & 268.1296 & 91.9636 & 15.3325 & 2018-12-03 & 6 & MSI & 80, 200 & 0.5 & 3.0020 & passive & y \\ \hline
        183 & 2020-038BL & SKYSAT-C14 & 20301.5324 & 53.0009 & 354.7150 & 0.00019990 & 291.6503 & 68.4295 & 15.5687 & 2020-06-13 & 6 & MSI & 80, 200 & 0.5 & 2.9529 & passive & y \\ \hline
        184 & 2020-038BN & SKYSAT-C15 & 20301.4483 & 53.0004 & 354.8934 & 0.00050680 & 209.2476 & 150.8251 & 15.5690 & 2020-06-13 & 6 & MSI & 80, 200 & 0.5 & 2.9529 & passive & y \\ \hline
        185 & 2020-038BM & SKYSAT-C16 & 20301.8754 & 53.0015 & 352.5843 & 0.00012940 & 48.6107 & 311.5014 & 15.5688 & 2020-06-13 & 6 & MSI & 80, 200 & 0.5 & 2.9529 & passive & y \\ \hline
        186 & 2020-057BQ & SKYSAT-C17 & 20301.7939 & 53.0000 & 92.1784 & 0.00100340 & 180.5095 & 179.5914 & 15.7203 & 2020-08-18 & 6 & MSI & 80, 200 & 0.5 & 1.9708 & passive & y \\ \hline
        187 & 2020-057BR & SKYSAT-C18 & 20301.5929 & 52.9952 & 90.0723 & 0.00089940 & 279.6382 & 80.3615 & 15.6447 & 2020-08-18 & 6 & MSI & 80, 200 & 0.5 & 4.9189 & passive & y \\ \hline
        188 & 2020-057BS & SKYSAT-C19 & 20301.7924 & 52.9987 & 91.4150 & 0.00026490 & 110.1355 & 249.9946 & 15.7150 & 2020-08-18 & 6 & MSI & 80, 200 & 0.5 & 7.3771 & passive & y \\ \hline
        189 & 2018-096M & BLACKSKY GLOBAL 1 & 20301.7880 & 97.4133 & 15.2542 & 0.00201060 & 25.3093 & 334.9127 & 15.2759 & 2018-11-29 & 3 & MSI & 30 & 0.9-1.1 & 15.0006 & passive & y \\ \hline
        190 & 2019-037C & BLACKSKY GLOBAL 3 & 20301.7981 & 45.0069 & 109.6440 & 0.00100530 & 250.3425 & 109.6378 & 15.3913 & 2019-06-29 & 3 & MSI & 30 & 0.9-1.1 & 14.7330 & passive & n \\ \hline
        191 & 2019-054E & BLACKSKY GLOBAL 4 & 20302.1475 & 45.0140 & 297.4708 & 0.00152540 & 202.2458 & 157.7760 & 15.1292 & 2019-08-19 & 3 & MSI & 30 & 0.9-1.1 & 15.0010 & passive & n \\ \hline
        192 & 2020-055BP & BLACKSKY GLOBAL 7 & 20301.8673 & 53.0062 & 255.7571 & 0.00025990 & 342.0424 & 18.0493 & 15.5396 & 2020-08-07 & 3 & MSI & 30 & 0.9-1.1 & 9.8400 & passive & n \\ \hline
        193 & 2020-055BQ & BLACKSKY GLOBAL 8 & 20301.9020 & 53.0065 & 255.9865 & 0.00029640 & 72.6858 & 287.4475 & 15.5392 & 2020-08-07 & 3 & MSI & 30 & 0.9-1.1 & 9.8403 & passive & n \\ \hline
        194 & 2016-040D & GHGSAT-D & 20303.9178 & 97.2945 & 358.3279 & 0.00106620 & 80.7785 & 279.4657 & 15.2324 & 2016-06-22 & 3 & SWIR & 15 & 50 & 8.9997 & passive & y \\ \hline
        195 & 2020-061G & GHGSAT-C1 & 20304.1600 & 97.4594 & 16.3066 & 0.00032760 & 120.2653 & 239.8905 & 15.1638 & 2020-09-03 & 3 & SWIR & 15 & 25 & 12.9998 & passive & y \\ \hline
        196 & 2016-033B & NUSAT-1 (FRESCO) & 20312.8669 & 97.4010 & 42.1696 & 0.00120570 & 305.0335 & 177.5235 & 15.2840 & 2016-05-30 & 4 & SWIR & 5, 150 & 1 & 10.9990 & passive & y \\ \hline
        197 & 2016-033C & NUSAT-2 (BATATA) & 20316.6762 & 97.4089 & 48.8266 & 0.00108150 & 284.2567 & 75.7473 & 15.3044 & 2016-05-30 & 4 & SWIR & 5, 150 & 1 & 16.9994 & passive & y \\ \hline
        198 & 2017-034C & NUSAT-3 (MILANESAT) & 20316.4505 & 43.0163 & 297.3433 & 0.00105500 & 258.3643 & 101.6019 & 15.1045 & 2017-06-15 & 4 & SWIR & 5, 150 & 1 & 6.8774 & passive & n \\ \hline
        199 & 2018-015D & NUSAT-4 (ADA) & 20316.6652 & 97.4608 & 84.5599 & 0.00159500 & 302.8970 & 57.0732 & 15.2488 & 2018-02-02 & 4 & SWIR & 5, 150 & 1 & 4.0029 & passive & y \\ \hline
        200 & 2018-015K & NUSAT-5 (MARYAM) & 20316.6334 & 97.4614 & 84.7992 & 0.00154900 & 305.3160 & 54.6628 & 15.2509 & 2018-02-02 & 4 & SWIR & 5, 150 & 1 & 4.0023 & passive & y \\ \hline
        201 & 2020-061A & NUSAT-6 (HYPATIA) & 20316.7570 & 97.3998 & 28.6036 & 0.00064200 & 332.6885 & 27.4013 & 15.2076 & 2020-09-03 & 4 & SWIR & 5, 150 & 1 & 5.0007 & passive & y \\ \hline
        202 & 2020-003B & NUSAT-7 (SOPHIE) & 20316.7417 & 97.2948 & 20.1997 & 0.00123920 & 280.2625 & 79.7218 & 15.2940 & 2020-01-15 & 4 & SWIR & 5, 150 & 1 & 7.0006 & passive & y \\ \hline
        203 & 2020-003C & NUSAT-8 (MARIE) & 20316.7330 & 97.3025 & 19.9696 & 0.00102270 & 283.4783 & 76.5316 & 15.2775 & 2020-01-15 & 4 & SWIR & 5, 150 & 1 & 14.9990 & passive & y \\ \hline
        204 & 2020-079A & NUSAT-9 (ALICE) & 20316.7388 & 97.2665 & 28.8406 & 0.00086550 & 220.5814 & 139.4783 & 15.3077 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 10.0015 & passive & y \\ \hline
        205 & 2020-079B & NUSAT-10 (CAROLINE) & 20316.7384 & 97.2699 & 28.8443 & 0.00074510 & 217.4892 & 142.5831 & 15.3088 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 10.0060 & passive & y \\ \hline
        206 & 2020-079C & NUSAT-11 (CORA) & 20316.7382 & 97.2661 & 28.8415 & 0.00081250 & 224.2093 & 135.8500 & 15.3093 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 10.0004 & passive & y \\ \hline
        207 & 2020-079D & NUSAT-12 (DOROTHY) & 20316.7376 & 97.2686 & 28.8445 & 0.00086260 & 232.5063 & 127.5395 & 15.3109 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 9.9994 & passive & y \\ \hline
        208 & 2020-079E & NUSAT-13 (EMMY) & 20316.7374 & 97.2687 & 28.8445 & 0.00081420 & 232.5608 & 127.4893 & 15.3116 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 9.9990 & passive & y \\ \hline
        209 & 2020-079F & NUSAT-14 (HEDY) & 20316.7376 & 97.2677 & 28.8433 & 0.00076010 & 227.2763 & 132.7839 & 15.3109 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 9.9994 & passive & y \\ \hline
        210 & 2020-079G & NUSAT-15 (KATHERINE) & 20316.7369 & 97.2689 & 28.8452 & 0.00074920 & 234.2810 & 125.7735 & 15.3128 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 9.9981 & passive & y \\ \hline
        211 & 2020-079H & NUSAT-16 (LISE) & 20316.7366 & 97.2672 & 28.8438 & 0.00079540 & 239.6202 & 120.4254 & 15.3138 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 9.9975 & passive & y \\ \hline
        212 & 2020-079J & NUSAT-17 (MARY) & 20316.7351 & 97.2678 & 28.8470 & 0.00071100 & 252.5356 & 107.5109 & 15.3178 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 12.9998 & passive & y \\ \hline
        213 & 2020-079K & NUSAT-18 (VERA) & 20316.7347 & 97.2686 & 28.8479 & 0.00072320 & 256.7143 & 103.3293 & 15.3190 & 2020-11-06 & 4 & SWIR & 5, 150 & 1 & 12.9988 & passive & y \\ \hline
        214 & 2016-040A & CARTOSAT-2C & 20330.0821 & 97.4298 & 27.1881 & 0.00141660 & 17.1691 & 69.9936 & 15.1929 & 2016-06-22 & 5 & PAN & 111, 168, 250 & 0.65, 2 & 10.9989 & passive & y \\ \hline
        215 & 2017-008A & CARTOSAT-2D & 20329.7039 & 97.4719 & 26.6527 & 0.00085670 & 147.2768 & 212.9000 & 15.1926 & 2017-02-15 & 5 & PAN & 111, 168, 250 & 0.65, 2 & 10.9993 & passive & y \\ \hline
        216 & 2017-036C & CARTOSAT-2E & 20329.9143 & 97.4026 & 25.6459 & 0.00081960 & 191.7617 & 168.3428 & 15.1930 & 2017-06-23 & 5 & PAN & 111, 168, 250 & 0.65, 2 & 10.9989 & passive & y \\ \hline
        217 & 2018-004A & CARTOSAT-2F & 20330.0899 & 97.3655 & 26.0333 & 0.00036860 & 196.7950 & 221.3843 & 15.1932 & 2018-01-12 & 5 & PAN & 111, 168, 250 & 0.65, 2 & 10.9989 & passive & y \\ \hline
        218 & 2019-081A & CARTOSAT-3 & 20330.1133 & 97.4764 & 29.4441 & 0.00150250 & 48.0576 & 39.5773 & 15.1921 & 2019-11-27 & 5 & PAN, MSI & 16, 111, 168, 250 & 0.28, 1.14 & 10.9996 & passive & y \\ \hline
        219 & 2017-042Y & LANDMAPPER-BC1 & 20329.2290 & 97.4988 & 205.5659 & 0.00107410 & 101.5373 & 258.7053 & 14.9228 & 2017-07-14 & 5 & MSI, HRMS & 220 & 22 & 10.9968 & passive & y \\ \hline
        220 & 2017-042X & LANDMAPPER-BC2 & 20329.9148 & 97.4984 & 206.0198 & 0.00111450 & 100.3800 & 259.8676 & 14.9217 & 2017-07-14 & 5 & MSI, HRMS & 220 & 22 & 10.9975 & passive & y \\ \hline
        221 & 2018-004H & LANDMAPPER-BC3 v2 & 20330.1483 & 97.4285 & 38.9845 & 0.00096190 & 199.8506 & 160.2358 & 15.2366 & 2018-01-12 & 5 & MSI, HRMS & 220 & 22 & 8.9975 & passive & y \\ \hline
        222 & 2018-099K & LANDMAPPER-BC4 & 20330.1804 & 97.6879 & 38.1950 & 0.00122000 & 17.7533 & 342.4112 & 14.9480 & 2018-12-03 & 5 & MSI, HRMS & 220 & 22 & 8.5014 & passive & y \\ \hline
        223 & 2018-014A & KANOPUS-V 3 & 20330.0438 & 97.4342 & 235.8097 & 0.00017410 & 79.6849 & 35.4997 & 15.1924 & 2018-02-01 & 5 & PAN, MSS, MSU & 20, 250 & 2.5, 12, 25 & 10.9993 & passive & y \\ \hline
        224 & 2018-014B & KANOPUS-V 4 & 20330.0831 & 97.4344 & 236.0149 & 0.00017890 & 85.6369 & 26.9948 & 15.1925 & 2018-02-01 & 5 & PAN, MSS, MSU & 20, 250 & 2.5, 12, 25 & 10.9993 & passive & y \\ \hline
        225 & 2018-111A & KANOPUS-V 5 & 20330.0957 & 97.4353 & 235.7809 & 0.00018830 & 95.9169 & 14.8420 & 15.1924 & 2018-02-01 & 5 & PAN, MSS, MSU & 20, 250 & 2.5, 12, 25 & 10.9993 & passive & y \\ \hline
        226 & 2018-111A & KANOPUS-V 5 & 20330.0957 & 97.4353 & 235.7809 & 0.00018830 & 95.9169 & 14.8420 & 15.1924 & 2018-12-27 & 5 & PAN, MSS, MSU & 20, 250 & 2.5, 12, 25 & 10.9993 & passive & y \\ \hline
        227 & 2018-111B & KANOPUS-V 6 & 20330.0703 & 97.4348 & 235.7941 & 0.00020650 & 101.4961 & 12.7734 & 15.1924 & 2018-12-27 & 5 & PAN, MSS, MSU & 20, 250 & 2.5, 12, 25 & 10.9993 & passive & y \\ \hline
        228 & 2018-002A & SUPERVIEW-1 03 & 20330.1074 & 97.4932 & 47.0438 & 0.00044820 & 294.5934 & 126.9738 & 15.1501 & 2018-01-09 & 8 & PAN, MS & 60 & 0.5, 2 & 7.0011 & passive & y \\ \hline
        229 & 2018-002B & SUPERVIEW-1 04 & 20330.4576 & 97.4937 & 47.5428 & 0.00108270 & 276.3091 & 94.1841 & 15.1501 & 2018-01-09 & 8 & PAN, MS & 60 & 0.5, 2 & 7.0011 & passive & y \\ \hline
        230 & 2018-070A & ICESAT-2 & 20330.1126 & 92.0019 & 104.6627 & 0.00035780 & 94.5855 & 265.5803 & 15.2826 & 2018-09-15 & 5 & GLAS & 6 & 0.7 &  & active & y \\ \hline
        231 & 2018-071B & NOVASAR 1 & 20330.4697 & 97.7408 & 223.8666 & 0.00083160 & 100.7189 & 259.5643 & 14.9490 & 2018-09-16 & 7 & SAR & 20, 50, 100, 200 & 6, 20, 40 &  & active & y \\ \hline
        232 & 2018-076A & SAOCOM 1A & 20330.4988 & 97.8869 & 154.3277 & 0.00013980 & 81.3764 & 278.7620 & 14.8216 & 2018-10-07 & 5 & SAR & 50, 400 & 7, 100 &  & active & y \\ \hline
        233 & 2019-015A & PRISMA & 20331.1514 & 97.8463 & 43.4673 & 0.00014380 & 81.2790 & 278.8573 & 14.8368 & 2019-03-22 & 5 & VNIR, SWIR, PAN, HSIS & 30, 60 & 5, 30 &  & passive & y \\ \hline
        234 & 2019-092A & CSG 1 & 20331.0896 & 97.8835 & 151.9095 & 0.00015870 & 76.7830 & 283.3577 & 14.8215 & 2019-03-22 & 7 & SAR & 10, 200 & 0.8, 6 &  & active & y \\ \hline
        236 & 2016-059C & ALSAT 1B & 20331.1222 & 97.9919 & 22.2949 & 0.00315530 & 161.2059 & 199.0330 & 14.6338 & 2016-09-26 & 5 & VNIR, MSI & 140, 600 & 12, 24 &  & passive & y \\ \hline
        237 & 2010-035D & ALSAT 2A & 20331.1444 & 97.9459 & 19.8627 & 0.00016810 & 84.7686 & 275.3717 & 14.6665 & 2010-07-12 & 5 & PAN, MSI & 17.5, 600 & 1.5, 6 &  & passive & y \\ \hline
        238 & 2016-059D & ALSAT 2B & 20331.1029 & 98.0438 & 36.5890 & 0.00015610 & 71.7453 & 288.3926 & 14.6661 & 2016-09-26 & 5 & PAN, MSI & 17.5, 600 & 1.5, 6 &  & passive & y \\ \hline
        239 & 2019-093E & CBERS 4A & 20331.2064 & 97.9461 & 46.1183 & 0.00014310 & 92.0678 & 268.0703 & 14.8152 & 2019-12-20 & 5 & MUXCam, WFI, WPM & 90, 960 & 2, 8, 16, 55 &  & passive & y \\ \hline
        240 & 2010-013A & CRYOSAT 2 & 20330.8033 & 92.0157 & 146.7721 & 0.00072290 & 40.1528 & 320.0212 & 14.5191 & 2010-04-08 & 3.5 & SIRAL & 15 & 250 &  & active & n \\ \hline
        241 & 2018-015F & GOMX-4A & 20331.1110 & 97.4581 & 98.8038 & 0.00173040 & 255.4923 & 278.7093 & 15.2481 & 2018-02-02 & 3 & VNIR & 200 & 70 &  & passive & y \\ \hline
        242 & 2018-015E & GOMX-4B & 20330.8975 & 97.4593 & 98.4474 & 0.00169850 & 254.6043 & 105.3318 & 15.2454 & 2018-02-02 & 3 & VNIR & 200 & 70 &  & passive & y \\ \hline
        243 & 2016-058A & PERUSAT 1 & 20331.1379 & 98.1998 & 41.5874 & 0.00014340 & 100.9963 & 259.1408 & 14.5857 & 2016-09-16 & 10 & VIS, NIR & 60 & 0.7, 2 &  & passive & y \\ \hline
        244 & 2007-061A & RADARSAT-2 & 20331.3279 & 98.5775 & 335.5475 & 0.00011580 & 94.4236 & 31.0215 & 14.2999 & 2007-12-14 & 7 & SAR & 14, 500 & 1, 100 &  & active & y \\ \hline
        245 & 2019-033A & RCM-1 & 20331.2627 & 97.7599 & 335.7058 & 0.00016700 & 84.0263 & 276.1135 & 14.9259 & 2019-06-12 & 7 & SAR & 14, 500 & 1, 100 &  & active & y \\ \hline
        246 & 2019-033C & RCM-2 & 20331.3076 & 97.7593 & 335.7991 & 0.00015690 & 88.5250 & 271.6151 & 14.9259 & 2019-06-12 & 7 & SAR & 14, 500 & 1, 100 &  & active & y \\ \hline
        247 & 2019-033B & RCM-3 & 20331.2854 & 97.7599 & 335.8235 & 0.00015160 & 80.8400 & 279.2989 & 14.9259 & 2019-06-12 & 7 & SAR & 14, 500 & 1, 100 &  & active & y \\ \hline
    %\end{tabular}
\end{longtable}

\end{document}